Syntax and Semantics of Abstract Binding Trees

### 2015-11-26 paper.tex
Add citations for schanuel / nominal sets stuff

Intuitively, when $\Upsilon$ supports $\Member{m}{X(\Upsilon')}$, we would
expect that we can work backward to a unique $\Of{m'}{\Upsilon}$ such that
$\IsEq{m'\varrho}{m}$; whilst this is not in general the case for presheaves
$X$, it is precisely the glueing condition for covariant sheaves on $\SCtx$
under the atomic topology. The sheaf condition, then, ensures that the notion
of support is well-behaved.

@@

\begin{remark}
  The presentation we have given above is related both to the Schanuel topos
  and, equivalently, Pitts' category of nominal sets; we differ only in
  discussing covariant sheaves on the category of symbol contexts $\SCtx$, as
  opposed to covariant sheaves on finite sets of symbols $\SymSets$ (i.e.\
  unisorted contexts).
\end{remark}

>>>>

Intuitively, when $\Upsilon$ supports $\Member{m}{X(\Upsilon')}$, we would
expect that we can work backward to a unique $\Of{m'}{\Upsilon}$ such that
$\IsEq{m'\varrho}{m}$; whilst this is not in general the case for presheaves
$X$, it is precisely the sheaf condition for covariant presheafs on $\SCtx$
under the atomic topology \cite[p.~126]{mac-lane-moerdijk:1992}. The sheaf condition, then, ensures that the notion
of support is well-behaved.

@@

\begin{remark}
  The presentation we have given above is related both to the Schanuel topos
  and, equivalently, Pitts' category of nominal sets \cite{fiore-staton:2006}; we differ only in
  discussing covariant sheaves on the category of symbol contexts $\SCtx$, as
  opposed to covariant sheaves on finite sets of symbols $\SymSets$ (i.e.\
  unisorted contexts).
\end{remark}
